Ten Simple Rules for Teaching Programming

### 2017-08-10 paper.tex
Corrected the description of peer instruction to state that the group discussion should always take place.

The best method developed so far for larger-scale classrooms is called Peer Instruction.
Originally created by Eric Mazur at Harvard~\cite{mazur-peer-instruction},
it has been studied extensively in a wide variety of contexts,
including programming \cite{porter-multi,porter-success}.
In simplified form,
peer instruction proceeds in three phases:

@@

\item Learners then vote on the answer to the question.

  \begin{itemize}
  \item If they all have the right answer, the instructor can move on.
  \item If they all have the same wrong answer,
    the instructor addresses that specific misconception.
  \item If they have a mix of right and wrong answers,
    they are given several minutes to discuss those answers with one another
    in small groups (typically 2-4 students)
    and then reconvene and vote again.
  \end{itemize}

>>>>

The best method developed so far for larger-scale classrooms is called Peer Instruction.
Originally created by Eric Mazur at Harvard~\cite{mazur-peer-instruction},
it has been studied extensively in a wide variety of contexts,
including programming \cite{porter-multi,porter-success}.
In simplified form,
peer instruction proceeds in several phases:

@@

\item Learners then vote on the answer to the question individually, thus formalising their initial prediction.

\item Learners are then given several minutes to discuss those answers with one another
    in small groups (typically 2-4 students)
    and then reconvene and vote again.
\item Then the instructor can act on the latest answers.
  \begin{itemize}
  \item If all the learners have the right answer, the instructor can move on.
  \item If some of the wrong answers remain popular after group discussion,
    the instructor can addresses those specific misconceptions directly or engage in class-wide discussion.
  \end{itemize}
